Figures

### 2020-03-03 manuscript/figures.Rmd
describe elpd in table caption

```{r 03_model_summary, results='asis', warning=FALSE, echo = FALSE}
knitr::kable('\\includegraphics[width=5in]{"../tables/03_model_summary"}', col.names = NULL, caption = "Diagnostics for each model listed by regionally varying coefficient. Table is sorted by decreasing R2 and expected log predictive density.")
```

>>>>

```{r 03_model_summary, results='asis', warning=FALSE, echo = FALSE}
knitr::kable('\\includegraphics[width=5in]{"../tables/03_model_summary"}', col.names = NULL, caption = "Diagnostics for each model listed by regionally varying coefficient. Table is sorted by decreasing $R^2$ and expected log predictive density (ELPD). ELPD has a similar interpretation to information criterion measures like AIC. Typically models are considered to be different if they are separated by an AIC value of greater than 2, which is equivalent to an ELPD value of -1.")
```
